---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  out.height = "150px"
)
library(knitr)
library(magrittr)
library(stringr)
library(dplyr)
```

# emlspice

Functions for translating EML into [`dataspice`](https://github.com/ropenscilabs/dataspice) tabular formats:

* **attributes.csv** - explains each of the variables in the dataset
* **biblio.csv** - for spatial and temporal coverage, dataset name, keywords, etc.
* **access.csv** - for files and file types
* **creators.csv** - for data authors

## Installation

```{r eval = FALSE}
devtools::install_github("isteves/dataspice")
```

## Example
```{r}
library(emlspice)
library(eml2)

eml_path <- system.file("LeConte_meteo_metadata.xml", package = "emlspice")
eml <- read_eml(eml_path)
```

Currently, there are 4 functions in the package, which each take an `emld` object (using `eml2::read_eml` and translates it to the dataspice tables.

Here are the first few lines of each tabular format:

```{r eval = FALSE}
es_attributes(eml)
```

```{r echo = FALSE}
es_attributes(eml) %>% head() %>% kable() 
```

```{r eval = FALSE}
es_access(eml)
```

```{r echo = FALSE}
es_access(eml) %>% head() %>% kable() 
```

```{r eval = FALSE}
es_biblio(eml)
```

```{r echo = FALSE}
es_biblio(eml) %>% 
    mutate(license = str_replace_all(license, "\n", "")) %>% 
    kable() 
```

```{r eval = FALSE}
es_creators(eml)
```

```{r echo = FALSE}
es_creators(eml) %>% head() %>% kable() 
```
